Adaptative neigbouring methods applied to telephonic base stations

### 2024-08-20 article.tex
beginning to remake the introduction

\begin{abstract}
  The field of telecommunication represents a gigantic mine of information, the smartphone penetration rate being 69\%
  in 2023 in the world, and 97\% in France. Therefore, the collected datas represent a big opportunity for telecommunication
  companies to predict their customers behaviour for internal or marketing purposes. Thus, it is primordial for these companies
  to be able to determinate if a user is moving. For that, it is necessary to understand the neighbouring relationships between the 
  telephonic base stations. This article aims at comparing different method, ellaborated in order to adaptively detect these
  relationship between telephonic base stations given their geographical positions.
\end{abstract}

\section{Introduction}
    \IEEEPARstart{T}{his} article is the continuation of the work done by Delphine Paquiry in this paper \cite{art_del_paq}.
    It aims at discovering the neighbouring relationships between base stations from their geographical positions, using a 
    measure of the density of base station.

    For that, it is necessary to describe and analyse the databases that have been used during the research, then to present 
    the different approaches that always consist of these steps: establish a first neighbouring graph, compute the base station 
    densities and filter this graph with different criteria using this information. The final step is to present the results
    of the different approaches and conclude.
\section{Related works}

>>>>

\begin{abstract}
    The field of telecommunication represents a gigantic mine of information, the smartphone penetration rate being 69\%
    in 2023 in the world, and 97\% in France. Therefore, the collected datas represent a big opportunity for telecommunication
    companies to predict their customers behaviour for internal or marketing purposes. Thus, it is primordial for these companies
    to be able to determine if a user is moving. For that, it is necessary to understand the neighbouring relationships between the 
    telephonic base stations. This article aims at proposing and comparing different method, that aim at adaptively detect these
    relationship between telephonic base stations. Therefore, it proposes a new method to create a neighbouring graph of base
    stations via their geographical positions.
\end{abstract}

\section{Introduction}
    \IEEEPARstart{T}{his} article articulates around the themes of mobile networks and neighbouring problems.

    A cellular network, also know as a mobile network, is a type of telecommunications network that is dispersed over geographical areas known 
    as cells, each of which is supplied by at least one fixed-location transceiver called base station. These base stations give the cell network
    coverage so that voice, data, and other kinds of content may be transmitted.

    Given a list of points and their coordinates, a neighbouring problem consists in finding, for each point, a list of other points that are 
    considered as its neighbours.

\section{Related works}
